Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2012-08-20 paper1.tex
Added new L=128 data.  Modified figures in the paper.  Still needs a bit more
minor scala edits.

%BPSK plots
%\begin{figure}[tp]
%	\centering
%		\includegraphics[width=\linewidth]{code/data/plotM2-1.mps}
%		\caption{Amplitude error for BPSK}
%		\label{fig:plotamp}
%\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM2-2.mps}
		\caption{Phase error for BPSK}
		\label{fig:plotphase}
\end{figure}

% \begin{figure*}[tp]
% 	\centering
%         \includegraphics{code/data/plotM2-3.mps}
% 		\caption{complex amplitude error for BPSK}
% 		\label{fig:plotcamp}
% \end{figure*}

%QPSK plots
%\begin{figure}[tp]
%	\centering
%		\includegraphics[width=\linewidth]{code/data/plotM4-1.mps}
%		\caption{Amplitude error for QPSK}
%		\label{fig:plotamp}
%\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM4-2.mps}
		\caption{Phase error for QPSK}
		\label{fig:plotphase}
\end{figure}

% \begin{figure}[tp]
% 	\centering
%         \includegraphics{code/data/plotM4-3.mps}
% 		\caption{complex amplitude error for QPSK}
% 		\label{fig:plotcamp}
% \end{figure}

%8PSK plots
%\begin{figure}[tp]
%	\centering
%		\includegraphics[width=\linewidth]{code/data/plotM8-1.mps}
%		\caption{Amplitude error for 8PSK}
%		\label{fig:plotamp}
%\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM8-2.mps}
		\caption{Phase error for 8PSK}
		\label{fig:plotphase}
\end{figure}

% \begin{figure}[tp]
% 	\centering
%         \includegraphics{code/data/plotM8-3.mps}
% 		\caption{complex amplitude error for 8PSK}
% 		\label{fig:plotcamp}
% \end{figure}

>>>>

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM2-2.mps}
		\caption{Phase error versus SNR for BPSK with $L=4096$.}
		\label{fig:plotphase}
\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM4-2.mps}
		\caption{Phase error versus SNR for QPSK with $L=4096$.}
		\label{fig:plotphase}
\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM8-2.mps}
		\caption{Phase error versus SNR for $8$-PSK with $L=4096$.}
		\label{fig:plotphase}
\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM2-1.mps}
		\caption{Unbiased amplitude error versus SNR for BPSK with $L=4096$.}
		\label{fig:plotphase}
\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM4-1.mps}
		\caption{Unbiased amplitude error versus SNR for QPSK with $L=4096$.}
		\label{fig:plotphase}
\end{figure}

\begin{figure}[tp]
	\centering
		\includegraphics[width=\linewidth]{code/data/plotM8-1.mps}
		\caption{Unbiased amplitude error versus SNR for $8$-PSK with $L=4096$.}
		\label{fig:plotphase}
\end{figure}
